---
title: "How to Run the Detention Report Pipeline"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

This document walks through the full pipeline that turns bi-weekly ICE
detention facility releases into the Interval ADP charts and HTML reports
published at [detentionreports.com](https://detentionreports.com/).

Every chunk below is set to `eval = FALSE` — this file is a **guide**, not a
script to knit end to end. Run each `source()` line yourself in the R console
(with `ice_detention_reports.Rproj` open, so working directory is correct),
checking the messages/warnings each step prints before moving to the next.

## 0. One-time setup

```{r}
install.packages(c(
  "tidyverse", "openxlsx", "readxl", "janitor", "stringr", "rlang",
  "rjson", "jsonlite", "here", "ggplot2", "scales", "patchwork",
  "extrafont", "cowplot", "magick", "quarto", "leaflet", "DT",
  "knitr", "kableExtra", "purrr", "lubridate"
))
```

Open `ice_detention_reports.Rproj` in RStudio before running anything —
every script uses relative paths from the project root.

## 1. Drop in the new release

Copy the new bi-weekly xlsx into `./DetentionFacilities/`. Sanity-check it
first:

- Are population values rounded oddly, or blank for any facility?
- Do the three category totals (classification / criminality / threat level)
  roughly agree?
- Note the release's "as of" date — you'll need it for the touchpoint edits
  in step 3.

## 2. Interval ADP + individualized subpopulation ADP

```{r}
source("interval_adp.r")             # -> final, latest_date, all_clean, output_clean
source("Individual_Internal_ADP.r")  # -> IntervalAdpForIndividualColumn_<date>_v1.xlsx
```

`interval_adp.r` reads **every** xlsx in `DetentionFacilities/`, not just the
newest one — that's what lets stale/historical facilities (step 6) still be
chartable later. `Individual_Internal_ADP.r` also joins in Owner / Operator /
Institutional Type from `ICE_Facility_Owner&Operator.xlsx`, keyed on
`DETLOC`.

**Known manual touchpoint:** if the new release resurrects a facility whose
`Name` collides across states (e.g. two different "Clinton County Jail"
entries, one NY one IN), check the `case_when(...)` DETLOC-override blocks in
`detloc_processing_2025-12-08.r` and `Individual_Internal_ADP.r` — add an
override there if the automatic join picks the wrong one.

## 3. Charts

Before running, update these hardcoded touchpoints for the new release date:

- `interval_adp_chartmaker.r`: none needed if using `run_pipeline.r` (dates
  are derived from `latest_date` automatically); when running standalone,
  `touchpoint_date` / `as_of_date` / `plots_folder` are set from the max pull
  date in `final`.
- Create the new output folder if it doesn't exist yet:
  `plots<YYYY_MM_DD>/` and `mandatory_plots<YYYY_MM_DD>/` — both scripts
  `dir.create()` these automatically, no manual step required.

```{r}
source("interval_adp_chartmaker.r")   # bar charts (plots<date>/) + ALOS scatter (plots7/)
source("MandatoryDetentionNumber.r")  # -> "mandatory detention with interval adp...xlsx"
source("mandatory_chartmaker.r")      # mandatory stacked charts (mandatory_plots<date>/)
```

Validate the chart count matches the facility count in the new release
before moving on.

## 4. Render HTML reports

```{r}
source("facilities_reporting.r")
```

This renders one HTML file per facility present in the **latest** release
(auto-detected by file mtime in `./DetentionFacilities/`), writing to
`./html/`. It also automatically:

- Resolves DETLOC via `detloc_2025-04-13.csv`, falling back to
  `ICE_Facility_Owner&Operator.xlsx` for anything not found there.
- Renders Clinton County Jail separately (its Name collides across states,
  so it's excluded from the main loop and handled by City-disambiguated
  join at the end of the script).

Two block toggles inside the script (comment one in, the other out):

- **ALL FACILITIES** (default/active) — renders every facility in the
  current release.
- **NEW CONTRACTS ONLY** — filters to `facility_with_new_contracts final.csv`;
  only use this if you specifically want a partial run for newly-contracted
  facilities.

## 5. Update the facility index

```{r}
source("generate_index.r")
```

Reads `old_index.json` + the newly computed `final`, writes `index.json` —
the metadata file the detentionreports.com site uses to list every facility
that's ever had a report. Facilities present in the old index are always
kept even if they're not in the newest release (see step 6 for why that
matters).

Optionally, to enrich the index with Owner/Operator/Institutional Type
without touching `index.json` itself:

```{r}
source("add_operator_info_to_index.r")  # -> index_with_operator_info.json
```

## 6. Stale / historical facilities

Because `index.json` accumulates every facility ever reported, and the
regular pipeline (steps 3–4) only processes facilities in the **latest**
release, facilities that drop out of recent releases stop getting new charts
and reports even though their pages are still live. These two scripts cover
that gap — run them **after** step 5, once `index.json` is current:

```{r}
source("stale_facilities_charts.r")     # bar + scatter + mandatory charts,
                                         # using each facility's OWN last pull date
source("stale_facilities_reporting.r")  # HTML reports for the same set
```

How they work:

- `stale_facilities_charts.r` diffs `index.json`'s DETLOCs against the
  latest release's DETLOCs. For each stale one, it pulls that facility's
  full history from `final` (which — per step 2 — already contains every
  release, not just the latest) and charts it using its own last-seen pull
  date, so the x-axis doesn't stretch out to the current touchpoint with a
  long empty gap.
- `stale_facilities_reporting.r` does the equivalent for HTML: it builds a
  small `IntervalAdpForStaleFacilities_<date>.xlsx` (each stale facility's
  row at its own last pull date), figures out which older
  `DetentionFacilities/*.xlsx` release that facility's metadata should come
  from, and renders the qmd with a `meta_xlsx` param override pointing at
  that older file.

To re-render just specific facilities instead of the whole stale set (e.g.
after fixing coordinates for one or two), set `only_detlocs` first:

```{r}
only_detlocs <- c("KANHOLD", "NRJDCVA")
source("stale_facilities_reporting.r")
```

**Missing coordinates:** both scripts skip (and log) any facility not found
in `src/facility_locations.csv`. Add a `Name, Address, City, State, Zip`
row there (Name must match the raw ALL-CAPS spelling from the relevant
`DetentionFacilities` release exactly) with latitude/longitude filled in,
then re-run.

## 7. Push HTML to GitHub

Push the contents of `./html/` to the reports repo. The historical guidance
was to push in batches of ≤13 files via GitHub Desktop — verify against
current repo settings/CI before assuming that limit still applies.

## Full pipeline in one shot

For a routine release with no new edge cases, `run_pipeline.r` chains steps
2–4:

```{r}
source("run_pipeline.r")
```

It does **not** run step 5 (`generate_index.r`) or step 6 (stale
facilities) — run those separately afterward.
